TODO: title

### 2014-04-22 paper/main.tex
more results work

      % explain strangeness of Item-Item
  Item-Item performs quite poorly in our cold start setting.
  Unlike the other algorithms Item-Item actually performs worse as it gets more ratings for the first few ratings.
  The explanation for this has to do with the coverage of the algorithm.
  Item-Item, unlike the other two algorithms, has relatively low coverage at cold start, needing around 8 ratings to reach 90 percent coverage. %TODO: check this

      % possibly coverage plot
      % true crossing point?
  % Recommendation quality metrics
    % NDCG
    % MAP, precision, recall plots 
    % explain results from MAP and precision
    % explain recall results
    % recall results, strangeness and popularity
    % popularity graph
    % TopN average rating / topn rmse
    % interpret graph and reason about what it means about quality
  % Other recommender metrics
    % diversity plot
    % talk about popularity and diversity
      % algos don't cross, and seem more straight, this seems to be more of a system wide choice than other metrics.***
      % relatively the same thing as each other.
      % upward diversity trend in baselines - seen items removed from recs => must increase diversity
      % we don't know best, but user user is probably too bad, and avg rating is probably too high SVD and Item-Item probably in a good zone.
      % user study would be needed to find out.
    % spread plot
      % by and far item-item has the best spread
      % user-user has good spread, but interestingly the spread gets worse
        % not sure why, perhaps as more ratings there is a regression to the mean sort of trend where more ratings means mroe neighbors available, means more ratings.
        % either way we don't see this as a good thing...
      % svd
        % spread seems a little low. like before we don't _know_, but it looks like svd might focus too much on a smaller list of items.
\section{Conclusions}
  % summary of results in a big old table.
    % the accuracy of svd and user-user both seemed good. item-item seemed to have trouble especially with very new users.
    % svd did quite well on our traditional topN metrics, item-item did OK, and user-user did bad., but there are flaws with these metrics.
    % on our topN RMSE item-item (again) seemed to have issues, and user-user did quite well, but the low hit rate is troubleing. 
    % again svd seems the winner here.
    % on our fluffy metrics item-item and svd seemed to do well. I might argue that item-item seemed to do better (spread, and higher throughout).
    % user-user seemed to do poor
  % what this means
    % user-user seems to be able to give accurate predictions, but seems to focus on overly obscure items in recommendation.
    % item-item seems to give not-bad recommendations, but its predictions have issues
    % based only on these results svd seems to be the best performer and is our recommendation to new systems.
  % other takeaways
    % regularization
    % if you use a switching recommender, this methodology can help you choose when to switch.
    % non-traditional metrics can tell you more about what is going on, these seem to be more properties of the class of algo than of the data, so its worth looking at these when choosing algorithms, to find one with properties that are good for your task.

>>>>

      % explain strangeness of Item-Item
  Item-Item performs quite poorly in the cold start setting.
  Until we have around 20 ratings the RMSE of Item-Item is worse than the item baseline.
  More interestingly, unlike the other algorithms Item-Item actually appears to performs worse as it gets more ratings for the first few ratings.

  The curve exhibited by Item-Item's RMSE is caused by two trends.
  First as the system revives more ratings, predictions from Item-Item are more accurate, leading to a downward trend.
  Secondly, as the system revives more ratings, Item-Item can make predictions for more items, meaning the fewer predictions are serviced by the baseline.
  Because the baseline is more accurate, this leads to an upward trend.
  Overall this leads to curved performance.
  If we were to compute RMSE only over the items where item-item can make a prediction we would see a curve similar to the other algorithms, but shifted up.
      % possibly coverage plot
      % true crossing point?

\subsection {Recommendatin quality metrics}
  % Recommendation quality metrics
    % NDCG
  Figure \ref{fig:ndcg} shows the algorithm's performance on the nDCG metric.
  The algorithm's behavior is essentially equivalent to the RMSE behavior.
  Again, User-User has a minor dip on very new users, but then tracks SVD in uniformly improving quite well from there.
  Likewise Item-Item exhibits the same dipped accuracy, although it doesn't catch up the baseline as fast.
  Unlike previous metrics, the item baseline, and the user-item baseline have the same performance.
  This is because nDCG is a ranking metric, not an accuracy metric.
  Because the user item baseline orders items the same way as the item baseline, both will have the same accuracy on any ranking metrics.

    % MAP, precision, fallout plots 
    % explain results from MAP and precision
    % explain recall results
    % recall results, strangeness and popularity

  Figure \ref{fig:map} shows MAP@20, precision@20, and fallout@20.
  All three metrics show essentially the same trend, User-User gets the lowest score, the baselines get the highest score.
  On both MAP@20 and precision@20 svd gets a higher score than Item-Item throughout, performing almost as highly as the baseline.
  On fallout@20 Item-Item performs higher than svd and the baseline, but decreases faster than bath, ending with a lower score than either. 
  We also tried recall@20 and mrr@20 and found the same trend.

  This result is rather strange as MAP and precision are metrics where high scores are good, where fallout is a metric where high scores are bad.
  This leads to an issue, these metrics contradict each other in terms of the quality of the recommendations from our algorithm.
  One possible reason for this is that these topN metrics are known to be biased by popular items (TODO: cite bellogin).
  Looking at the average popularity (figure \ref{fig:pop})of recommended items, we see that this seems to explain most of the variance in these metrics.
  Therefore we seek a different metric to analyze the quality of the recommendations.

  Figure \ref{fig:topN.rmse}
    % TopN average rating / topn rmse
    % interpret graph and reason about what it means about quality
  % Other recommender metrics
    % popularity graph
    % diversity plot
    % talk about popularity and diversity
      % algos don't cross, and seem more straight, this seems to be more of a system wide choice than other metrics.***
      % relatively the same thing as each other.
      % upward diversity trend in baselines - seen items removed from recs => must increase diversity
      % we don't know best, but user user is probably too bad, and avg rating is probably too high SVD and Item-Item probably in a good zone.
      % user study would be needed to find out.
    % spread plot
      % by and far item-item has the best spread
      % user-user has good spread, but interestingly the spread gets worse
        % not sure why, perhaps as more ratings there is a regression to the mean sort of trend where more ratings means mroe neighbors available, means more ratings.
        % either way we don't see this as a good thing...
      % svd
        % spread seems a little low. like before we don't _know_, but it looks like svd might focus too much on a smaller list of items.
\section{Conclusions}
  % summary of results in a big old table.
    % the accuracy of svd and user-user both seemed good. item-item seemed to have trouble especially with very new users.
    % svd did quite well on our traditional topN metrics, item-item did OK, and user-user did bad., but there are flaws with these metrics.
    % on our topN RMSE item-item (again) seemed to have issues, and user-user did quite well, but the low hit rate is troubleing. 
    % again svd seems the winner here.
    % on our fluffy metrics item-item and svd seemed to do well. I might argue that item-item seemed to do better (spread, and higher throughout).
    % user-user seemed to do poor
  % what this means
    % user-user seems to be able to give accurate predictions, but seems to focus on overly obscure items in recommendation.
    % item-item seems to give not-bad recommendations, but its predictions have issues
    % based only on these results svd seems to be the best performer and is our recommendation to new systems.
  % other takeaways
    % regularization
    % if you use a switching recommender, this methodology can help you choose when to switch.
    % non-traditional metrics can tell you more about what is going on, these seem to be more properties of the class of algo than of the data, so its worth looking at these when choosing algorithms, to find one with properties that are good for your task.
